### 2017-03-13 thesis/misc/appendix2.tex
Need to add linear model prediction scatter plots - tmp commit

	\begin{figure}[htpb]
		\centering
		\includegraphics[width=0.7\linewidth]{results2/gatzares1}
		\caption{results from gatza's study}
		\label{fig:gatza_paper_res}
	\end{figure}

	% [1] "crolgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

	% Coefficients:
	%              Estimate Std. Error t value Pr(>|t|)
	% (Intercept)         0.553214  0.123891 4.465  2.16e-05 ***
	% bmi                 -0.001629 0.004071 -0.400 0.69
	% (Intercept)         0.55700   0.05464  10.194 <2e-16   ***
	% bmiStatusobese      -0.10551  0.07021  -1.503 0.136
	% bmiStatusoverweight -0.02165  0.07727  -0.280 0.780
	% (Intercept)         0.307513  0.163530 1.880  0.0631   .
	% bmi                 0.011279  0.006976 1.617  0.1092
	% bmiStatusobese      -0.261145 0.118795 -2.198 0.0304   *
	% bmiStatusoverweight -0.079845 0.084661 -0.943 0.3480
	% (Intercept)         0.007141  0.382725 0.019  0.9852
	% bcat_probes         0.156062  0.223779 0.697  0.4873
	% er_probes           0.123403  0.254800 0.484  0.6293
	% ifna_probes         -0.430229 0.497301 -0.865 0.3892
	% ifng_probes         0.378437  0.509352 0.743  0.4594
	% myc_probes          0.160785  0.229142 0.702  0.4846
	% pr_probes           0.597403  0.244252 2.446  0.0164   *
	% (Intercept)         0.055088  0.389472 0.141  0.8878
	% bmi                 -0.002745 0.003814 -0.720 0.4736
	% bcat_probes         0.179900  0.226799 0.793  0.4297
	% er_probes           0.125413  0.255485 0.491  0.6247
	% ifna_probes         -0.475417 0.502546 -0.946 0.3466
	% ifng_probes         0.429131  0.515526 0.832  0.4074
	% myc_probes          0.184642  0.232124 0.795  0.4284
	% pr_probes           0.607982  0.245336 2.478  0.0151   *
	% (Intercept)         0.01666   0.37989  0.044  0.9651
	% bmiStatusobese      -0.11197  0.06602  -1.696 0.0933   .
	% bmiStatusoverweight -0.02348  0.07151  -0.328 0.7434
	% bcat_probes         0.22035   0.22616  0.974  0.3325
	% er_probes           0.10450   0.25330  0.413  0.6809
	% ifna_probes         -0.60343  0.50372  -1.198 0.2341
	% ifng_probes         0.54671   0.51484  1.062  0.2911
	% myc_probes          0.21341   0.22998  0.928  0.3559
	% pr_probes           0.59491   0.24257  2.453  0.0161   *
	% (Intercept)         -0.128149 0.393204 -0.326 0.7453
	% bmi                 0.008834  0.006565 1.346  0.1819
	% bmiStatusobese      -0.234634 0.112386 -2.088 0.0397   *
	% bmiStatusoverweight -0.067942 0.078484 -0.866 0.3890
	% bcat_probes         0.216892  0.225167 0.963  0.3380
	% er_probes           0.081506  0.252745 0.322  0.7478
	% ifna_probes         -0.625864 0.501740 -1.247 0.2155
	% ifng_probes         0.546873  0.512538 1.067  0.2889
	% myc_probes          0.196215  0.229305 0.856  0.3945
	% pr_probes           0.560706  0.242816 2.309  0.0232   *

	% [1] "resobsgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

	% Coefficients:
	%              Estimate Std. Error t value Pr(>|t|)
	% (Intercept)         0.547104  0.123915 4.415  2.62e-05 ***
	% bmi                 -0.001422 0.004072 -0.349 0.728
	% (Intercept)         0.547619  0.054641 10.022 <2e-16   ***
	% bmiStatusobese      -0.096832 0.070212 -1.379 0.171
	% bmiStatusoverweight -0.001804 0.077273 -0.023 0.981
	% (Intercept)         0.298589  0.163546 1.826  0.0710   .
	% bmi                 0.011259  0.006976 1.614  0.1099
	% bmiStatusobese      -0.252186 0.118807 -2.123 0.0364   *
	% bmiStatusoverweight -0.059898 0.084669 -0.707 0.4810
	% (Intercept)         0.18694   0.36963  0.506  0.6142
	% bcat_probes         0.09717   0.21612  0.450  0.6541
	% er_probes           0.07879   0.24608  0.320  0.7496
	% ifna_probes         -0.17576  0.48029  -0.366 0.7152
	% ifng_probes         0.07930   0.49193  0.161  0.8723
	% myc_probes          -0.04517  0.22130  -0.204 0.8387
	% pr_probes           0.59554   0.23590  2.525  0.0133   *
	% (Intercept)         0.221757  0.376612 0.589  0.5574
	% bmi                 -0.001994 0.003688 -0.540 0.5902
	% bcat_probes         0.114479  0.219311 0.522  0.6029
	% er_probes           0.080247  0.247050 0.325  0.7461
	% ifna_probes         -0.208580 0.485954 -0.429 0.6688
	% ifng_probes         0.116119  0.498505 0.233  0.8163
	% myc_probes          -0.027845 0.224460 -0.124 0.9015
	% pr_probes           0.603222  0.237235 2.543  0.0127   *
	% (Intercept)         0.195965  0.367384 0.533  0.5951
	% bmiStatusobese      -0.096834 0.063844 -1.517 0.1328
	% bmiStatusoverweight -0.004412 0.069155 -0.064 0.9493
	% bcat_probes         0.150379  0.218719 0.688  0.4935
	% er_probes           0.058880  0.244961 0.240  0.8106
	% ifna_probes         -0.344126 0.487134 -0.706 0.4817
	% ifng_probes         0.242697  0.497893 0.487  0.6271
	% myc_probes          -0.001285 0.222407 -0.006 0.9954
	% pr_probes           0.591191  0.234582 2.520  0.0135   *
	% (Intercept)         0.041459  0.379420 0.109  0.9132
	% bmi                 0.009426  0.006335 1.488  0.1403
	% bmiStatusobese      -0.227717 0.108446 -2.100 0.0386   *
	% bmiStatusoverweight -0.051853 0.075733 -0.685 0.4953
	% bcat_probes         0.146687  0.217273 0.675  0.5013
	% er_probes           0.034350  0.243884 0.141  0.8883
	% ifna_probes         -0.368065 0.484150 -0.760 0.4491
	% ifng_probes         0.242870  0.494570 0.491  0.6246
	% myc_probes          -0.019634 0.221267 -0.089 0.9295
	% pr_probes           0.554701  0.234304 2.367  0.0201   *

	% [1] "rescrolgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

	% Coefficients:
	%               Estimate Std. Error t value Pr(>|t|)
	% (Intercept)         0.5343899  0.1239554 4.311  3.9e-05 ***
	% bmi                 -0.0009922 0.0040730 -0.244 0.808
	% (Intercept)         0.54870    0.05482   10.009 <2e-16  ***
	% bmiStatusobese      -0.09063   0.07044   -1.287 0.201
	% bmiStatusoverweight -0.01515   0.07753   -0.195 0.845
	% (Intercept)         0.304200   0.164179  1.853  0.0670  .
	% bmi                 0.011054   0.007003  1.578  0.1178
	% bmiStatusobese      -0.243160  0.119267  -2.039 0.0442  *
	% bmiStatusoverweight -0.072189  0.084997  -0.849 0.3978
	% (Intercept)         0.17069    0.37929   0.450  0.6537
	% bcat_probes         0.09532    0.22177   0.430  0.6683
	% er_probes           0.03171    0.25251   0.126  0.9004
	% ifna_probes         -0.57965   0.49283   -1.176 0.2426
	% ifng_probes         0.50919    0.50478   1.009  0.3157
	% myc_probes          0.06345    0.22708   0.279  0.7805
	% pr_probes           0.54200    0.24206   2.239  0.0276  *
	% (Intercept)         0.204758   0.386507  0.530  0.5976
	% bmi                 -0.001950  0.003785  -0.515 0.6076
	% bcat_probes         0.112257   0.225072  0.499  0.6192
	% er_probes           0.033134   0.253540  0.131  0.8963
	% ifna_probes         -0.611750  0.498720  -1.227 0.2231
	% ifng_probes         0.545210   0.511601  1.066  0.2894
	% myc_probes          0.080405   0.230357  0.349  0.7279
	% pr_probes           0.549516   0.243468  2.257  0.0264  *
	% (Intercept)         0.17933    0.37777   0.475  0.636
	% bmiStatusobese      -0.09681   0.06565   -1.475 0.144
	% bmiStatusoverweight -0.01219   0.07111   -0.171 0.864
	% bcat_probes         0.14969    0.22490   0.666  0.507
	% er_probes           0.01354    0.25189   0.054  0.957
	% ifna_probes         -0.73888   0.50091   -1.475 0.144
	% ifng_probes         0.66381    0.51197   1.297  0.198
	% myc_probes          0.10813    0.22869   0.473  0.638
	% pr_probes           0.53872    0.24121   2.233  0.028   *
	% (Intercept)         0.027729   0.390580  0.071  0.9436
	% bmi                 0.009248   0.006522  1.418  0.1596
	% bmiStatusobese      -0.225233  0.111636  -2.018 0.0466  *
	% bmiStatusoverweight -0.058734  0.077961  -0.753 0.4532
	% bcat_probes         0.146066   0.223664  0.653  0.5154
	% er_probes           -0.010526  0.251058  -0.042 0.9667
	% ifna_probes         -0.762373  0.498391  -1.530 0.1296
	% ifng_probes         0.663981   0.509117  1.304  0.1955
	% myc_probes          0.090122   0.227775  0.396  0.6933
	% pr_probes           0.502919   0.241196  2.085  0.0399  *

	% [1] "caobsgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

	% Coefficients:
	%              Estimate Std. Error t value Pr(>|t|)
	% (Intercept)         0.538968  0.123943 4.349  3.39e-05 ***
	% bmi                 -0.001147 0.004073 -0.282 0.779
	% (Intercept)         0.53896   0.05458  9.875  2.76e-16 ***
	% bmiStatusobese      -0.08982  0.07013  -1.281 0.203
	% bmiStatusoverweight 0.01804   0.07719  0.234  0.816
	% (Intercept)         0.27986   0.16317  1.715  0.0896   .
	% bmi                 0.01171   0.00696  1.683  0.0957   .
	% bmiStatusobese      -0.25146  0.11853  -2.121 0.0365   *
	% bmiStatusoverweight -0.04241  0.08447  -0.502 0.6168
	% (Intercept)         0.12454   0.38803  0.321  0.7490
	% bcat_probes         0.14068   0.22688  0.620  0.5367
	% er_probes           0.11597   0.25833  0.449  0.6545
	% ifna_probes         -0.33319  0.50420  -0.661 0.5104
	% ifng_probes         0.30871   0.51641  0.598  0.5515
	% myc_probes          -0.04569  0.23232  -0.197 0.8445
	% pr_probes           0.56692   0.24764  2.289  0.0243   *
	% (Intercept)         0.162063  0.395326 0.410  0.6828
	% bmi                 -0.002148 0.003872 -0.555 0.5804
	% bcat_probes         0.159335  0.230208 0.692  0.4906
	% er_probes           0.117547  0.259326 0.453  0.6514
	% ifna_probes         -0.368552 0.510101 -0.723 0.4718
	% ifng_probes         0.348376  0.523276 0.666  0.5072
	% myc_probes          -0.027017 0.235613 -0.115 0.9090
	% pr_probes           0.575201  0.249024 2.310  0.0232   *
	% (Intercept)         0.134514  0.384960 0.349  0.7276
	% bmiStatusobese      -0.099695 0.066899 -1.490 0.1397
	% bmiStatusoverweight 0.008987  0.072463 0.124  0.9016
	% bcat_probes         0.193430  0.229183 0.844  0.4009
	% er_probes           0.092451  0.256681 0.360  0.7196
	% ifna_probes         -0.522336 0.510440 -1.023 0.3089
	% ifng_probes         0.492130  0.521713 0.943  0.3481
	% myc_probes          -0.001892 0.233048 -0.008 0.9935
	% pr_probes           0.560583  0.245805 2.281  0.0249   *
	% (Intercept)         -0.028482 0.397505 -0.072 0.9430
	% bmi                 0.009944  0.006637 1.498  0.1376
	% bmiStatusobese      -0.237770 0.113616 -2.093 0.0392   *
	% bmiStatusoverweight -0.041061 0.079343 -0.518 0.6061
	% bcat_probes         0.189535  0.227630 0.833  0.4073
	% er_probes           0.066573  0.255509 0.261  0.7950
	% ifna_probes         -0.547591 0.507227 -1.080 0.2832
	% ifng_probes         0.492312  0.518143 0.950  0.3446
	% myc_probes          -0.021250 0.231813 -0.092 0.9272
	% pr_probes           0.522087  0.245472 2.127  0.0362   *

	% [1] "cacrolgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

	% Coefficients:
	%               Estimate Std. Error t value Pr(>|t|)
	% (Intercept)         5.062e-01  1.240e-01 4.083  9.16e-05 ***
	% bmi                 -3.953e-05 4.074e-03 -0.010 0.992
	% (Intercept)         0.52453    0.05485   9.564  1.29e-15 ***
	% bmiStatusobese      -0.06411   0.07047   -0.910 0.365
	% bmiStatusoverweight 0.02958    0.07756   0.381  0.704
	% (Intercept)         0.273274   0.164135  1.665  0.0992   .
	% bmi                 0.011360   0.007001  1.622  0.1080
	% bmiStatusobese      -0.220856  0.119235  -1.852 0.0671   .
	% bmiStatusoverweight -0.029032  0.084974  -0.342 0.7334
	% (Intercept)         0.02932    0.40048   0.073  0.9418
	% bcat_probes         0.23660    0.23416   1.010  0.3150
	% er_probes           0.09521    0.26662   0.357  0.7218
	% ifna_probes         -0.49129   0.52037   -0.944 0.3476
	% ifng_probes         0.44466    0.53298   0.834  0.4063
	% myc_probes          0.16111    0.23977   0.672  0.5033
	% pr_probes           0.49566    0.25558   1.939  0.0555   .
	% (Intercept)         0.051698   0.408467  0.127  0.8996
	% bmi                 -0.001281  0.004000  -0.320 0.7495
	% bcat_probes         0.247720   0.237861  1.041  0.3004
	% er_probes           0.096149   0.267946  0.359  0.7205
	% ifna_probes         -0.512383  0.527057  -0.972 0.3335
	% ifng_probes         0.468320   0.540670  0.866  0.3887
	% myc_probes          0.172240   0.243445  0.708  0.4811
	% pr_probes           0.500601   0.257301  1.946  0.0548   .
	% (Intercept)         0.03806    0.39931   0.095  0.9243
	% bmiStatusobese      -0.07973   0.06939   -1.149 0.2536
	% bmiStatusoverweight 0.02249    0.07516   0.299  0.7655
	% bcat_probes         0.27648    0.23772   1.163  0.2479
	% er_probes           0.07298    0.26625   0.274  0.7846
	% ifna_probes         -0.66043   0.52946   -1.247 0.2155
	% ifng_probes         0.60854    0.54116   1.125  0.2638
	% myc_probes          0.19456    0.24173   0.805  0.4230
	% pr_probes           0.48849    0.25497   1.916  0.0586   .
	% (Intercept)         -0.123986  0.412743  -0.300 0.7646
	% bmi                 0.009886   0.006892  1.434  0.1549
	% bmiStatusobese      -0.216997  0.117971  -1.839 0.0692   .
	% bmiStatusoverweight -0.027267  0.082384  -0.331 0.7414
	% bcat_probes         0.272606   0.236356  1.153  0.2518
	% er_probes           0.047249   0.265304  0.178  0.8591
	% ifna_probes         -0.685542  0.526672  -1.302 0.1964
	% ifng_probes         0.608724   0.538006  1.131  0.2609
	% myc_probes          0.175314   0.240700  0.728  0.4683
	% pr_probes           0.450215   0.254882  1.766  0.0808   .

	% [1] "caresobsgene"

	% Call:
	% lm(formula = as.formula(formula_txt[j]), data = data)

>>>>

	\section{Ranking method for the pathway associated genetic signatures}
	\label{sec:ranking_method_for_the_pathway_associated_genetic_signatures}

	To determine whether it was the best to rank the metagene scores based on the number of samples or rank the scores with the probit method, the two ranking methods were compared in scatter plots with the GT pathway metagenes in \gls{rma} or \gls{mas} normalised GT data.
	Since the results from the \gls{rma} and \gls{mas} normalised GT data were so similar to one another, only the results from the \gls{rma} normalised data are presented (\cref{fig:appendix/rank_scatter}).
	\cref{fig:appendix/rank_scatter} showed that the metagene scores for all of the GT pathway associated genetic signatures were approximately the same in either of the ranking methods used.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\caption[]{Scatter plots comparing the GT pathway metagenes ranked with probit and ranked based on number of samples in \gls{rma} normalised GT data. }
		\label{fig:appendix/rank_scatter}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=13]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=14]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=15]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\includegraphics[width=0.32\linewidth,page=16]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=17]{appendix/gatza_rma_meta_rank_vs_probit}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/gatza_rma_meta_rank_vs_probit}\\
		\vspace{1em}
		\caption[]{figure}
	\end{figure}

	\section{Normalisation method for the pathway associated genetic signature transformation matrices}
	\label{sec:normalisation_method_for_pathway_associated_genetic_signature_transformation_matrices}

	To investigate whether the normalisation methods were important in the creation of the pathway associated genetic signature transformation matrices, and whether the normalisation methods of the data affected the resulting metagenes, transformation matrices were generated in \gls{rma} or \gls{mas} normalised GT data set and then applied to the \gls{rma} or \gls{mas} normalised GT data set.
	The results in \cref{fig:appendix/gt_meta_rma_mas} showed less variability of the metagene scores when the metagenes were derived from the data with the same normalisation method (for example, metagenes derived from \gls{rma} normalised data), regardless of the transformation matrix used to produce the metagenes.
	This was most clearly demonstrated by the \gls{bcat}, \gls{er}, \gls{ifna}, \gls{ifny}, p53 and \gls{pr} pathway associated genetic signatures.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=7]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=8]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=9]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=10]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=11]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=12]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{Scatter plots comparing the GT pathway metagenes derived from the transformation matrices (TM) in \gls{rma} or \gls{mas} normalised GT data set.
		All of the transformation matrices were generated in either the \gls{rma} or \gls{mas} normalised GT data set.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=13]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=14]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=15]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=16]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=17]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=18]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=19]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=20]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=21]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=22]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=23]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=24]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=25]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=26]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=27]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=28]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=29]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=30]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=31]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=32]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=33]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=34]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=35]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=36]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=37]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=38]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=39]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=40]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=41]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=42]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=43]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=44]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=45]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=46]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=47]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=48]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=49]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=50]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=51]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=52]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=53]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=54]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=55]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=56]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=57]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=58]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=59]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=60]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=61]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=62]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=63]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=64]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=65]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=66]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=67]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=68]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=69]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=70]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=71]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=72]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=73]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=74]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=75]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=76]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=77]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=78]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=79]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=80]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=81]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=82]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=83]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=84]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=85]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=86]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=87]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=88]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=89]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=90]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=91]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=92]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=93]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=94]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=95]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=96]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\begin{figure}[htpb]
		\ContinuedFloat
		\captionsetup{list=off,format=cont}
		\centering
		\includegraphics[width=0.32\linewidth,page=97]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=98]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=99]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=100]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=101]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=102]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=103]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=104]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=105]{appendix/allmeta_rma_vs_mas}\\
		\includegraphics[width=0.32\linewidth,page=106]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=107]{appendix/allmeta_rma_vs_mas}
		\includegraphics[width=0.32\linewidth,page=108]{appendix/allmeta_rma_vs_mas}\\
		\caption[]{figure}
	\end{figure}

	\newpage

	\section{Additional results used to determine the directionality of the pathway metagenes}
	\label{sec:additional_results_to_determine_the_directionality_of_the_pathway_metagenes}

	The directionality of the pathway metagenes were determined by comparing the metagene values with the gene expression of the representative gene for the pathway associated genetic signature, as well as the gene expression pattern of the pathway signature (\cref{fig:appendix/gt_meta_rma_mas}).
	Together with the original results presented by \citet{Gatza2010a} (\cref{sec:result_from_gatza2010a_study}), the final directions of the pathway metagenes were decided.

	\begin{figure}[htp!]
		\centering
		\includegraphics[width=0.32\linewidth,page=1]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=2]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=3]{appendix/gtrmastdrank}\\
		\includegraphics[width=0.32\linewidth,page=4]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=5]{appendix/gtrmastdrank}
		\includegraphics[width=0.32\linewidth,page=6]{appendix/gtrmastdrank}\\
		\caption[]{Heatmaps showing the gene expression of the pathway associated genetic signatures, pathway metagenes, and the expression of the representative pathway gene in \gls{rma} normalised GT data set.
		For each pathway associated genetic signature, the gene expression pattern of the signature was plotted in the heatmap.
		The expression of the representative gene for the pathway signature (see \cref{tab:metagene_direction} in \cref{sub:metagene_direction}) was plotted seaparately as a bar above the pathway metagene scores.
		}
		\label{fig:appendix/gt_meta_rma_mas}
	\end{figure}
